\tool

### 2018-05-03 paper/paper.tex
Related work updates

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors. Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.

@@

%Learning in SE
Previous research has examined techniques to improve how software engineers learn new information. Cockburn and Williams studied the software engineering practice of \textit{pair programming}, and found that 84\% of participants found the practice to be beneficial for increasing knowledge and helped them learn `` faster and better because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}.  Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to create visual Python tutorials to improve information presented to learners~\cite{Gordon2015Codepourri}. Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determine how developers debug and propose software engineering tools integrate this process into their workflow~\cite{FlemingReactiveInformationForaging}. This project also seeks to improve software engineer learning, however our approach specifically aims to increase awareness of useful software engineering tools to help developers in their work.

%Other existing approaches
Researchers have also developed approaches to improve recommendations to software engineers. Fischer and colleagues encourage the use of \textit{active help systems} to guide users over passive help systems that require users to explicitly seek help~\cite{Fischer1984ActiveHelpSystems}. Cao and colleagues introduced \textit{idea gardening}, an approach for helping end-user programmers overcome barriers. Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}. Our work builds on research in this area by introducing a distinctive recommendation approach with three original design principles to make tool suggestions to developers more effective.

%Other existing tools
More specifically, researchers and toolsmiths have developed automated recommender systems to increase awareness of software engineering tools.  Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}.  SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. To improve the effectiveness of automated system-to-user recommendations, we implemented \tool~to evaluate our novel approach based on design principles derived from user-to-user recommendations.

%Other existing evaluations
Existing research has also focused on different recommendation styles for software engineering tools. Murphy-Hill and colleagues outlined existing ways to make recommendations to present and evaluate new algorithms based on collaborative filtering and feature discovery~\cite{Murphy-HillDeveloperFluency}. Winters and colleagues analyzed different styles of tool recommendationsand found that suggestion style impacts tool adoption for software developers~\cite{Mike Winters}. This research introduces a brand new recommendation style and measures the effectiveness of our approach by comparing it to other various styles of recommendations.

@@

Research suggests recommendations between colleagues is the most effective mode of tool discovery. Murphy-Hill and colleagues interviewed software engineers and found that, even though they appear less frequently in the workplace, developers prefer peer interactions over system-to-user recommendations.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

>>>>

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{Cao2010Debugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{Murphy-HillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors. Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{Murphy-Hill2011PeerInteraction}.

@@

% Recommendations in Software
Many researchers have developed approaches to try to solve the tool adoption problem for software users. Fischer and colleagues suggest passive help systems, which require software users to explicitly seek information, are ineffective and inconventient, and \textit{active help systems} designed to automatically guide and support users in their work are more effective~\cite{Fischer1984ActiveHelpSystems}. Passive recommendation approaches such as \textit{organizational memory} implemented in \textsc{Answer Garden}~\cite{Ackerman1990AnswerGarden}, \textit{group memory} in TeamInfo~\cite{Berlin1993TeamInfo}, and \textit{idea gardening}~\cite{Cao2011IdeaGarden} by Cao and colleagues use social and collaborative means to improve tool adoption and help software users overcome barriers. Other active solutions like Maltzahn's prototype recommender system \textsc{ToolBox}~\cite{Maltzahn1994Toolbox}, CommunityCommands by Matejka and colleagues\cite{Matejka2009CommunityCommands}, and Linton and colleagues' \textit{organization-wide learning} (OWL) technique~\cite{Linton2000OWL} monitor software actions by users by tracking logs on networked computers or stored in a database to suggest helpful commands and strategies to other users performing similar tasks. This research also aims to improve tool adoption among software users. To do improve the effectiveness of software recommendations, we introduce a new approach with three unique design principles and implement this approach in a novel active help system, \tool, that focuses on suggesting software engineering tools to developers.

%Recommendations to developers
More specifically, researchers have created techniques to improve the tool adoption problem among software engineers. Dubois and Tamburrelli argue that \textit{gamification} can motivate software engineers to adopt new tools and better software development practices~\cite{Dubois2013Gamification}, and this has been implemented in systems such as Blaze~\cite{Snipes2014Blaze}, HALO~\cite{Sheth2011Halo}, and Teamfeed~\cite{Singer2012Teamfeed}. Latoza and colleagues suggest \textit{crowdsourcing} is also beneficial for software engineering\cite{Latoza2016Crowdsourcing}. This has been used by researchers to improve developer learning and feature adoption in systems like Codepourri for Python tutorials~\cite{Gordon2015Codepourri}, CrowdStudy for web applications~\cite{Nebeling2013CrowdStudy}, and platforms such as TopCoder\cite{Lakhani2010TopCoder}. Our work builds on research in this area by introducing a distinctive recommendation approach with three original design principles to make tool suggestions to developers more effective.

%Other existing tools
Furthermore, researchers and toolsmiths have developed automated recommender systems to increase awareness of software engineering tools. SpyGlass automatically monitors developer actions, infers navigation tasks, and recommends tools to help users navigate code more efficiently~\cite{Viriyakattiyaporn2010Spyglass}. Systems such as Review Bot by Balachandran~\cite{BalachandranReviewBot} and Tricorder by Sadowski and colleagues~\cite{SadowskiTricorder} seek to improve adoption of program analysis in industry by automatically running static analysis tools and presenting the output to software engineers during code reviews and project builds. To improve the effectiveness of automated system-to-user recommendations, we implemented \tool~to evaluate our recommendation approach based on design principles derived from user-to-user recommendations. Additionally, this is the first approach to our knowledge that can be extended to recommend different types of software engineering tools to developers and that can be utilized by other researchers to increase awareness of their work.

%Other existing evaluations
Finally, existing research has also analyzed different types and styles of software engineering tool recommendations. Murphy-Hill and colleagues outlined existing recommendation algorithms to propose new algorithms based on the previous methods~\cite{Murphy-Hill2011Fluency}. Moreover, Murphy-Hill explored seven different methods of tool recommendations: peer observations, peer recommendations, tool encounters, tutorials, written descriptions, Twitter or RSS Feeds, and discussion threads- and found that peer interactions (peer observation and recommendation) were the most effective mode of tool discovery among software engineers~\cite{Murphy-Hill2011PeerInteraction, Murphy-Hill2015HowDoUsers}. Piorkowski and colleagues evaluated different recommendation algorithms to determine if \textit{information foraging theory}~\cite{Pirolli1999IFT} can be applied to improve recommendations using structure and wording based on how software engineers seek information~\cite{Piorkowski2012ReactiveIFT}. Additionally, Winters and colleagues analyzed different styles of tool recommendations and found that suggestion style impacts tool adoption for software developers [Mike]. This study compares the effectiveness of our approach to other recommender styles by modifying our design principles to investigate different wording and methods of communication in tool recommendations to developers.

@@

Research suggests recommendations between colleagues is the most effective mode of tool discovery. Murphy-Hill and colleagues interviewed software engineers and found that, even though they appear less frequently in the workplace, developers prefer peer interactions over system-to-user recommendations.~\cite{Murphy-Hill2011PeerInteraction}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.
